Estimating duration in the presence of misclassification

### 2024-03-11 biology-data.tex
fix subscripts for survival analysis

The crucial features of an infection episode are the start and end times of the infection.
Ignoring misclassified test results, latent start time of infection episode $i$, $B_i$, can be bounded as between the day after the last negative test, $l_i^{(b)}$, and the day of the first positive test, $r_i^{(b)}$.
Similarly, the latent end time of infection episode $i$, $E_i$, can be bounded as between the day of the last positive test, $l_i^{(e)}$, and the day before the following negative test, $r_i^{(e)}$.

>>>>

The crucial features of an infection episode are the start and end times of the infection.
Ignoring misclassified test results, latent start time of infection episode $j$, $B_j$, can be bounded as between the day after the last negative test, $l_j^{(b)}$, and the day of the first positive test, $r_j^{(b)}$.
Similarly, the latent end time of infection episode $i$, $E_j$, can be bounded as between the day of the last positive test, $l_j^{(e)}$, and the day before the following negative test, $r_j^{(e)}$.

### 2024-03-11 cis-imperfect-testing.tex
fix ref
fix subscripts for survival analysis

Comparing repeated data simulations, using the setup of \cref{E-perf-test:sec:simulation-study}, to the observed CIS data, suggests that this is due to the high frequency of single positive episodes in the CIS data (compare the histogram with $\psens=1$ and the vertical line in \cref{imperf-test:fig:sim-single-pos}).
A single positive episode is an episode containing exactly one positive test; intuitively, these cause estimates to be shorter because the lower bound on the length of time the episode is 1 day, the shortest possible.
Specifically, if $i$ is a single positive episode then $i$'s admissible region (as defined in \cref{E-perf-test:sec:model}) includes $b_i = e_i = r_i^{(b)} = l_i^{(e)}$.
In this case, the beginning and end day of the episode are both equal to the day of this one positive test.
If this is true, then the duration is $d_i = e_i - b_i + 1 = 1$.
Additionally, short episodes are very likely to be missed, which means that the design of the CIS cannot rule out many of them occurring.
% This produced the same pattern, that is estimating too many short episodes (not shown).

@@

First, in \cref{imperf-test:sec:modifying-p_ia}, I modify $p_{ia}$, the probability episode $i$ being admissible, to allow for the episode possibly being longer than observed.
Then, in \cref{imperf-test:sec:modifying-p_iu}, I modify $p_{iu}$, the probability episode $i$ being undetected, to allow for additional episodes being missed.

@@

\todo[inline]{Proof-read the following paragraphs (up until cases). Also check indices: is $i$ indexing individuals, episodes, or schedules?}
I start by finding the tests that need consideration.
For tractability and simplicity, I consider only tests between the negative tests providing an upper bound on the length of the episode.
By definition (see\todo{insert where these are defined in chapter 2}), these are the tests between $l_i^{(b)} - 1$ and $r_i^{(e)} + 1$ inclusive.
They are a subset of $\sched_i$, the set of test times for the individual in which episode $i$ occurs.

For tractability, assume that the negative test bounding the start of the episode, on day $l_i^{(b)}-1$, is a true negative.
This assumption is reasonable because, since a positive test follows at $r_i^{(b)}$, the negative at $l_i^{(b)}-1$ is likely early in the infection and the test sensitivity is high early in an infection.
Therefore, this is unlikely to be a false negative because, if the individual was detectable at this time, they are in a period with high test sensitivity.
This true negative, occurs with probability 1, and hence does not contribute to the likelihood.
Denote the remaining tests considered as $\sched'_i = \{ t \in \sched_i \ssep r_i^{(b)} \leq t \leq r_i^{(e)} + 1 \}$, and their results by $\vec{y_i} = \{ y_i(t) \ssep t \in \sched'_i \}$ where $y_i(t) = 1$ if the test on day $t$ is positive and 0 otherwise.

As I assume that there are no false positives, the infection episode must span at least the period $[r^{(b)}_i, l^{(e)}_i]$ because it starts and ends with a positive test.
This includes all $t \in \sched'_i$ except $t = r_i^{(e)}+1$.
Therefore, the test results at times in $\sched_i'$, except the test at $r_i^{(e)}+1$, are either true positives or false negatives.

Consider the negative test at $r_i^{(e)}+1$, the first negative after the start of the episode which may be a false negative.
It is a false negative if and only if the episode ends after the test, \ie $e_i > r_i^{(e)}$.
I proceed by considering whether this is the case, and considering the case with $b_i$ known; $b_i$ will later be integrated out.

First, if $e_i \leq r_i^{(e)}$, meaning that the test at $r_i^{(e)}+1$ is a true negative and the end of the episode is interval-censored as in the previous chapter.
% In this case, the test at $r_i^{(e)} + 1$ is a true negative, as are all other tests not in $\sched'_i$.
The true negative occurs with probability 1, by the assumption of no false positives.
\begin{align}
&p(\vec{y_i}, e_i \leq r_i^{(e)} | b_i, p_\text{sens}, \theta) \\
&= p(\vec{y_i}, l_i^{(e)} \leq e_i \leq r_i^{(e)} | t_i, b_i, p_\text{sens}, \theta) \\ % &\text{as no false positives}
&= p(\vec{y_i} \mid l_i^{(e)} \leq e_i \leq r_i^{(e)}, t_i, b_i, p_\text{sens}, \theta) p(l_i^{(e)} \leq e_i \leq r_i^{(e)} | t_i, b_i, p_\text{sens}, \theta) \\
&= \left( \prod_{t \in \sched'_i} p_\text{sens}^{y_i(t)} (1 - p_\text{sens})^{(1 - y_i(t))} \right) \left( S_\theta(l_i^{(e)} - b_i - 1) - S_\theta(r_i^{(e)} - b_i - 1) \right)
\label{imperf-test:eq:ll-ei-lt-ri}
\end{align}

Second, if $e_i > r_i^{(e)}$.
In this case, the test at $r_i^{(e)}$ is a false negative, occurring with probability $(1 - p_\text{sens})$.
To avoid having to consider tests after $r_i^{(e)}$, which could greatly complicate the likelihood, I model this case as the episode being right-censored at $r_i^{(e)}$.
Taking the same approach as before:
\begin{align}
&p(\vec{y_i}, e_i > r_i^{(e)} | b_i, p_\text{sens}, \theta) \\
&= p(\vec{y_i} \mid e_i > r_i^{(e)}, t_i, b_i, p_\text{sens}, \theta) p(e_i > r_i^{(e)} | t_i, b_i, p_\text{sens}, \theta) \\
&= \left( \prod_{t \in \sched'_i} p_\text{sens}^{y_i(t)} (1 - p_\text{sens})^{(1 - y_i(t))} \right) (1 - p_\text{sens}) S_\theta(r_i^{(e)} - b_i - 1)
\label{imperf-test:eq:ll-ei-gt-ri}
\end{align}

These expressions can now be used to form the full replacement for $p_{ia}$, $p'_{ia}$, the likelihood of the data $\vec{y_i}$.
First, augment the data with $b_i$, and split into the cases just discussed:
\begin{align}
p_{ia}'
&= p(\vec{y_i} \mid p_\text{sens}, \theta) \\
&= \sum_{b_i = l_i^{(b)}}^{r_i^{(b)}} \left( p(\vec{y_i}, e_i \leq r_i^{(e)} \mid b_i, p_\text{sens}, \theta) + p(\vec{y_i}, e_i > r_i^{(e)} \mid b_i, p_\text{sens}, \theta) \right) p(b_i \mid p_\text{sens}, \theta).
\intertext{Now, substitute in \cref{imperf-test:eq:ll-ei-lt-ri,imperf-test:eq:ll-ei-gt-ri}, then take out the common factor:}
&= \left( \prod_{t \in \sched'_i} p_\text{sens}^{y_i(t)} (1 - p_\text{sens})^{(1 - y_i(t))} \right) \\ & \ \times \sum_{b_i = l_i^{(b)}}^{r_i^{(b)}} \left( S_\theta(l_i^{(e)} - b_i - 1) - S_\theta(r_i^{(e)} - b_i - 1) + (1 - p_\text{sens}) S_\theta(r_i^{(e)} - b_i - 1) \right) \\ & \ \times p(b_i \mid p_\text{sens}, \theta) \\
&= \left( \prod_{t \in \sched'_i} p_\text{sens}^{y_i(t)} (1 - p_\text{sens})^{(1 - y_i(t))} \right) \\ & \ \times \sum_{b_i = l_i^{(b)}}^{r_i^{(b)}} \left( S_\theta(l_i^{(e)} - b_i - 1) - p_\text{sens} S_\theta(r_i^{(e)} - b_i - 1) \right) p(b_i \mid p_\text{sens}, \theta).
\label{imperf-test:eq:pia-prime}
\end{align}
Note that if $p_\text{sens} = 1$ then $p_{ia}' = p_{ia}$.

If $\psens$ is fixed (\ie has a point prior) and $p(b_i \mid \psens, \theta) \propto 1$ (as assumed in \cref{E-perf-test}) then:
\begin{align}
p_{ia}'
&\propto \sum_{b_i = l_i^{(b)}}^{r_i^{(b)}} S_\theta(l_i^{(e)} - b_i - 1) - p_\text{sens} S_\theta(r_i^{(e)} - b_i - 1).
\label{imperf-test:eq:pia-prime-constant}
\end{align}

@@

Several mechanisms for episodes being undetected were considered when deriving $p_{iu}$ in \cref{E-perf-test:eq:piu}.
I now consider the additional mechanisms arising due to false negatives.
Specifically, episode $i$ could be undetected if the first test after the $b_i$, episode $i$'s start day, is a false negative and then there are no subsequent positive tests.

This false negative would occur at the first test after the infection episode begins, on day $b_i + \tau_{\sched_i}(b_i)$ (see \cref{E-perf-test:sec:model}).
A false negative occurring requires that the episode has not yet ended but a negative still occurs.
The episode has not yet ended at the time of the test if $e_i = b_i + d_i - 1$ is after the test, that is the duration of the infection $d_i > \tau_{\sched_i}(b_i)$.
Conditional on the episode having not yet ended, the test result is negative with probability $1 - \psens$.

For there to be no subsequent positive tests, all tests up until day $e_i$ are false negatives.
I assume there is a negligible probability of two false negatives.
Therefore, this can only occur if the episode ends before another test.
Denote the number of days between $b_i$ and the test following the false negative as $\tau^2_{\sched_i}(b_i) \stackrel{\text{def}}{=} \tau_{\sched_i}(\tau_{\sched_i}(b_i) + 1)$.
Then, the episode ends before this test if $d_i < \tau^2_{\sched_i}(b_i)$.

Therefore, this mechanism causes episode $i$ to be undetected if all the following conditions hold.
\begin{enumerate}
    \item The episode would have been detected considering only the mechanisms in \cref{E-perf-test:eq:piu}. That is $b_i > \min(\sched_i)$ and $\tau_{\sched_i}(b_i) + b_i \leq e_i$.
    \item The episode ends in the interval $[\tau_{\sched_i}(b_i) + b_i, \tau^2_{\sched_i}(b_i) + b_i]$.
      Note that the lower bound here is exactly the bound on $e_i$ in the previous condition.
      Equivalently, $\tau_{\sched_i}(b_i) + 1 \leq d_i \leq \tau^2_{\sched_i}(b_i) + 1$.
    \item A false negative occurs on day $\tau_{\sched_i}(b_i) + b_i$. Conditional on the previous condition, this occurs with probability $1 - \psens$.
\end{enumerate}

The probability of this occurring, conditional on $B_i = b_i > \min(\sched_i)$ is:
\begin{align}
&\prob \left(
    \tau_{\sched_i}(b_i) + 1 \leq D_i \leq \tau^2_{\sched_i}(b_i) + 1
    \mid b_i,
\theta \right) (1 - \psens) \\
&= \left( S_\theta(\tau_{\sched_i}(b_i) + 1) - S_\theta(\tau^2_{\sched_i}(b_i) + 1) \right) (1 - \psens).
\end{align}
Integrating over $b_i$ for $\min \sched_i < b_i \leq T$ ($T$ being the last day of the period considered), in the same way as \cref{E-perf-test:eq:piu}, gives:
\begin{align}
\eta = (1 - p_\text{sens})\frac{1}{T} \sum_{b=\min(\sched_i) + 1}^T \left( S_\theta(\tau_{\sched_i}(b) + 1) - S_\theta(\tau^2_{\sched_i}(b) + 1) \right).
\end{align}

>>>>

Comparing repeated data simulations, using the setup of \cref{E-perf-test:sec:simulation-study}, to the observed CIS data, suggests that this is due to the high frequency of single positive episodes in the CIS data (compare the histogram with $\psens=1$ and the vertical line in \cref{imperf-test:fig:sim-single-pos}).
A single positive episode is an episode containing exactly one positive test; intuitively, these cause estimates to be shorter because the lower bound on the length of time the episode is 1 day, the shortest possible.
Specifically, if $j$ is a single positive episode then $j$'s admissible region (as defined in \cref{E-perf-test:sec:model}) includes $b_j = e_j = r_j^{(b)} = l_j^{(e)}$.
In this case, the beginning and end day of the episode are both equal to the day of this one positive test.
If this is true, then the duration is $d_j = e_j - b_j + 1 = 1$.
Additionally, short episodes are very likely to be missed, which means that the design of the CIS cannot rule out many of them occurring.
% This produced the same pattern, that is estimating too many short episodes (not shown).

@@

First, in \cref{imperf-test:sec:modifying-p_ia}, I modify $p_{ia}$, the probability of an episode with test schedule $i$ being admissible, to allow for the episode possibly being longer than observed.
Then, in \cref{imperf-test:sec:modifying-p_iu}, I modify $p_{iu}$, the probability of an episode with test schedule $i$ being undetected, to allow for additional episodes being missed.

@@

I start by finding the tests that need consideration.
For tractability and simplicity, I consider only tests between the negative tests providing an upper bound on the length of the episode.
By definition (see \cref{E-biology-data:sec:cis-episodes}), these are the tests between $l_{j(i)}^{(b)} - 1$ and $r_{j(i)}^{(e)} + 1$ inclusive.
They are a subset of $\sched_i$, the set of test times for the individual in which episode $i$ occurs.

For tractability, assume that the negative test bounding the start of the episode, on day $l_{j(i)}^{(b)}-1$, is a true negative.
This assumption is reasonable because, since a positive test follows at $r_{j(i)}^{(b)}$, the negative at $l_{j(i)}^{(b)}-1$ is likely early in the infection and the test sensitivity is high early in an infection.
Therefore, this is unlikely to be a false negative because, if the individual was detectable at this time, they are in a period with high test sensitivity.
This true negative, occurs with probability 1, and hence does not contribute to the likelihood.
Denote the remaining tests considered as $\sched'_i = \{ t \in \sched_i \ssep r_{j(i)}^{(b)} \leq t \leq r_{j(i)}^{(e)} + 1 \}$, and their results by $\vec{y_{j(i)}} = \{ y_{j(i)}(t) \ssep t \in \sched'_i \}$ where $y_{j(i)}(t) = 1$ if the test on day $t$ is positive and 0 otherwise.

As I assume that there are no false positives, the infection episode must span at least the period $[r^{(b)}_{j(i)}, l^{(e)}_{j(i)}]$ because it starts and ends with a positive test.
This includes all $t \in \sched'_i$ except $t = r_{j(i)}^{(e)}+1$.
Therefore, the test results at times in $\sched_i'$, except the test at $r_{j(i)}^{(e)}+1$, are either true positives or false negatives.

Consider the negative test at $r_{j(i)}^{(e)}+1$, the first negative after the start of the episode which may be a false negative.
It is a false negative if and only if the episode ends after the test, \ie $e_{j(i)} > r_{j(i)}^{(e)}$.
I proceed by considering whether this is the case, and considering the case with $b_{j(i)}$ known; $b_{j(i)}$ will later be integrated out.

First, if $e_{j(i)} \leq r_{j(i)}^{(e)}$, meaning that the test at $r_{j(i)}^{(e)}+1$ is a true negative and the end of the episode is interval-censored as in the previous chapter.
% In this case, the test at $r_{j(i)}^{(e)} + 1$ is a true negative, as are all other tests not in $\sched'_i$.
The true negative occurs with probability 1, by the assumption of no false positives.
\begin{align}
&p(\vec{y_{j(i)}}, e_{j(i)} \leq r_{j(i)}^{(e)} | b_{j(i)}, p_\text{sens}, \theta) \\
&= p(\vec{y_{j(i)}}, l_{j(i)}^{(e)} \leq e_{j(i)} \leq r_{j(i)}^{(e)} | t_i, b_{j(i)}, p_\text{sens}, \theta) \\ % &\text{as no false positives}
&= p(\vec{y_{j(i)}} \mid l_{j(i)}^{(e)} \leq e_{j(i)} \leq r_{j(i)}^{(e)}, t_i, b_{j(i)}, p_\text{sens}, \theta) p(l_{j(i)}^{(e)} \leq e_{j(i)} \leq r_{j(i)}^{(e)} | t_i, b_{j(i)}, p_\text{sens}, \theta) \\
&= \left( \prod_{t \in \sched'_i} p_\text{sens}^{y_{j(i)}(t)} (1 - p_\text{sens})^{(1 - y_{j(i)}(t))} \right) \left( S_\theta(l_{j(i)}^{(e)} - b_{j(i)} - 1) - S_\theta(r_{j(i)}^{(e)} - b_{j(i)} - 1) \right)
\label{imperf-test:eq:ll-ei-lt-ri}
\end{align}

Second, if $e_{j(i)} > r_{j(i)}^{(e)}$.
In this case, the test at $r_{j(i)}^{(e)}$ is a false negative, occurring with probability $(1 - p_\text{sens})$.
To avoid having to consider tests after $r_{j(i)}^{(e)}$, which could greatly complicate the likelihood, I model this case as the episode being right-censored at $r_{j(i)}^{(e)}$.
Taking the same approach as before:
\begin{align}
&p(\vec{y_{j(i)}}, e_{j(i)} > r_{j(i)}^{(e)} | b_{j(i)}, p_\text{sens}, \theta) \\
&= p(\vec{y_{j(i)}} \mid e_{j(i)} > r_{j(i)}^{(e)}, t_i, b_{j(i)}, p_\text{sens}, \theta) p(e_{j(i)} > r_{j(i)}^{(e)} | t_i, b_{j(i)}, p_\text{sens}, \theta) \\
&= \left( \prod_{t \in \sched'_i} p_\text{sens}^{y_{j(i)}(t)} (1 - p_\text{sens})^{(1 - y_{j(i)}(t))} \right) (1 - p_\text{sens}) S_\theta(r_{j(i)}^{(e)} - b_{j(i)} - 1)
\label{imperf-test:eq:ll-ei-gt-ri}
\end{align}

These expressions can now be used to form the full replacement for $p_{ia}$, $p'_{ia}$, the likelihood of the data $\vec{y_{j(i)}}$.
First, augment the data with $b_{j(i)}$, and split into the cases just discussed:
\begin{align}
p_{ia}'
&= p(\vec{y_{j(i)}} \mid p_\text{sens}, \theta) \\
&= \sum_{b_{j(i)} = l_{j(i)}^{(b)}}^{r_{j(i)}^{(b)}} \left( p(\vec{y_{j(i)}}, e_{j(i)} \leq r_{j(i)}^{(e)} \mid b_{j(i)}, p_\text{sens}, \theta) + p(\vec{y_{j(i)}}, e_{j(i)} > r_{j(i)}^{(e)} \mid b_{j(i)}, p_\text{sens}, \theta) \right) p(b_{j(i)} \mid p_\text{sens}, \theta).
\intertext{Now, substitute in \cref{imperf-test:eq:ll-ei-lt-ri,imperf-test:eq:ll-ei-gt-ri}, then take out the common factor:}
&= \left( \prod_{t \in \sched'_i} p_\text{sens}^{y_{j(i)}(t)} (1 - p_\text{sens})^{(1 - y_{j(i)}(t))} \right) \\ & \ \times \sum_{b_{j(i)} = l_{j(i)}^{(b)}}^{r_{j(i)}^{(b)}} \left( S_\theta(l_{j(i)}^{(e)} - b_{j(i)} - 1) - S_\theta(r_{j(i)}^{(e)} - b_{j(i)} - 1) + (1 - p_\text{sens}) S_\theta(r_{j(i)}^{(e)} - b_{j(i)} - 1) \right) \\ & \ \times p(b_{j(i)} \mid p_\text{sens}, \theta) \\
&= \left( \prod_{t \in \sched'_i} p_\text{sens}^{y_{j(i)}(t)} (1 - p_\text{sens})^{(1 - y_{j(i)}(t))} \right) \\ & \ \times \sum_{b_{j(i)} = l_{j(i)}^{(b)}}^{r_{j(i)}^{(b)}} \left( S_\theta(l_{j(i)}^{(e)} - b_{j(i)} - 1) - p_\text{sens} S_\theta(r_{j(i)}^{(e)} - b_{j(i)} - 1) \right) p(b_{j(i)} \mid p_\text{sens}, \theta).
\label{imperf-test:eq:pia-prime}
\end{align}
Note that if $p_\text{sens} = 1$ then $p_{ia}' = p_{ia}$.

If $\psens$ is fixed (\ie has a point prior) and $p(b_{j(i)} \mid \psens, \theta) \propto 1$ (as assumed in \cref{E-perf-test}) then:
\begin{align}
p_{ia}'
&\propto \sum_{b_{j(i)} = l_{j(i)}^{(b)}}^{r_{j(i)}^{(b)}} S_\theta(l_{j(i)}^{(e)} - b_{j(i)} - 1) - p_\text{sens} S_\theta(r_{j(i)}^{(e)} - b_{j(i)} - 1).
\label{imperf-test:eq:pia-prime-constant}
\end{align}

@@

Several mechanisms for episodes being undetected were considered when deriving $p_{iu}$ in \cref{E-perf-test:eq:piu}.
I now consider the additional mechanisms arising due to false negatives.
Specifically, episode $i$ could be undetected if the first test after the $b_{j(i)}$, episode $i$'s start day, is a false negative and then there are no subsequent positive tests.

This false negative would occur at the first test after the infection episode begins, on day $b_{j(i)} + \tau_{\sched_i}(b_{j(i)})$ (see \cref{E-perf-test:sec:model}).
A false negative occurring requires that the episode has not yet ended but a negative still occurs.
The episode has not yet ended at the time of the test if $e_{j(i)} = b_{j(i)} + d_i - 1$ is after the test, that is the duration of the infection $d_i > \tau_{\sched_i}(b_{j(i)})$.
Conditional on the episode having not yet ended, the test result is negative with probability $1 - \psens$.

For there to be no subsequent positive tests, all tests up until day $e_{j(i)}$ are false negatives.
I assume there is a negligible probability of two false negatives.
Therefore, this can only occur if the episode ends before another test.
Denote the number of days between $b_{j(i)}$ and the test following the false negative as $\tau^2_{\sched_i}(b_{j(i)}) \stackrel{\text{def}}{=} \tau_{\sched_i}(\tau_{\sched_i}(b_{j(i)}) + 1)$.
Then, the episode ends before this test if $d_i < \tau^2_{\sched_i}(b_{j(i)})$.

Therefore, this mechanism causes episode $i$ to be undetected if all the following conditions hold.
\begin{enumerate}
    \item The episode would have been detected considering only the mechanisms in \cref{E-perf-test:eq:piu}. That is $b_{j(i)} > \min(\sched_i)$ and $\tau_{\sched_i}(b_{j(i)}) + b_{j(i)} \leq e_{j(i)}$.
    \item The episode ends in the interval $[\tau_{\sched_i}(b_{j(i)}) + b_{j(i)}, \tau^2_{\sched_i}(b_{j(i)}) + b_{j(i)}]$.
      Note that the lower bound here is exactly the bound on $e_{j(i)}$ in the previous condition.
      Equivalently, $\tau_{\sched_i}(b_{j(i)}) + 1 \leq d_i \leq \tau^2_{\sched_i}(b_{j(i)}) + 1$.
    \item A false negative occurs on day $\tau_{\sched_i}(b_{j(i)}) + b_{j(i)}$. Conditional on the previous condition, this occurs with probability $1 - \psens$.
\end{enumerate}

The probability of this occurring, conditional on $B_{j(i)} = b_{j(i)} > \min(\sched_i)$ is:
\begin{align}
&\prob \left(
    \tau_{\sched_i}(b_{j(i)}) + 1 \leq D_i \leq \tau^2_{\sched_i}(b_{j(i)}) + 1
    \mid b_{j(i)},
\theta \right) (1 - \psens) \\
&= \left( S_\theta(\tau_{\sched_i}(b_{j(i)}) + 1) - S_\theta(\tau^2_{\sched_i}(b_{j(i)}) + 1) \right) (1 - \psens).
\end{align}
Integrating over $b_{j(i)}$ for $\min \sched_i < b_{j(i)} \leq T$ ($T$ being the last day of the period considered), in the same way as \cref{E-perf-test:eq:piu}, gives:
\begin{align}
\eta = (1 - p_\text{sens})\frac{1}{T} \sum_{b=\min(\sched_i) + 1}^T \left( S_\theta(\tau_{\sched_i}(b) + 1) - S_\theta(\tau^2_{\sched_i}(b) + 1) \right).
\end{align}
